### 2021-03-08 text/draft.tex
refactor structure

@@

\hypertarget{edoc-and-data-extraction}{%
\subsection{Edoc and data extraction}\label{edoc-and-data-extraction}}

Edoc is the institutional repository of the University of Basel. It was
conceived in 2009 as repository for electronic dissertations and grew in
scope when the University of Basel adapted its first open access policy
in 2013. As per today Edoc contains roughly 68'000 items. Edoc runs on
the EPrints 3 document management system
(https://github.com/eprints/eprints).

Even though Edoc is a public server, its database does not have a
web-ready API. In addition, since Edoc is a production server, its
underlying database cannot be used directly on pain of disturbing the
provided services. The data hence needs to be extracted from Edoc in
order to work with it. This could for example be achieved by cloning the
database of the server and running it on a local machine. However, this
route was not available due to the limited resources of the responsible
co-workers. I thus employed a workaround: Edoc has a built-in advanced
search tool where the results can be exported. Even though it is not
possible to extract all database items by default, only one of the many
available search fields has to be filled in. The complete database can
hence be extracted by only filling in the \texttt{Date} field and using
a sufficiently permissive time period such as 1940 to 2020 since the
oldest record in the database was published in 1942. On January 21 2021,
this query yielded 68'345 results. These results were then exported as a
326 MB JSON file called \texttt{1942-2020.json}. \texttt{1942-2020.json}
has two drawbacks. First, the maximum file size on GitHub is 100 MB. And
second, \texttt{1942-2020.json} is too big to be handled by standard
editors requiring special editors such as Oxygen. For these reasons
\texttt{1942-2020.json} was split into smaller files that are easier
handled and can be uploaded to GitHub. For this
\texttt{Utility.split\_json} was used yielding 14 files of size 20 MB or
less containing 5000 or fewer entries each. These files are called
\texttt{raw\_master\_x-y.json} (where x and y indicate the entries as
given by \texttt{1942-2020.json}) and saved under \texttt{/edoc/raw}.

\hypertarget{data-description-and-analysis}{%
\subsection{Data description and
analysis}\label{data-description-and-analysis}}

!! Explain the Edoc data fields. Say perhaps something about the
granularity of the relevant fields. Say something about how the fields
are filled in (and by whom).

@@

In this section, I will explain how the sample data set is selected and
constructed. ``Selection'' means the task of specifying a subset of the
Edoc data and ``construction'' means the task of implementing this
selection.

@@

The first constraint is that each item in the sample data set needs to
have a text. Intuitively, this text could consist of a title, an
abstract, or even a full text, or any combination of the above. Similar
to manual indexing, having more information (that is, longer texts)
usually implies a higher indexing quality in machine indexing. However,
this assumption needs to be confirmed empirically for the given machine
indexing framework and data set. If indeed confirmed, it might be
advisable only to index items that have a certain minimal text length.
Therefore, in order to construct the sample data set, we require each
item to have a non-empty value in the data fields \texttt{title},
\texttt{abstract}, and \texttt{id\_number} as proxy to retrieve a full
text remotely. Note that even more context could be provided by taking
into account other data fields such as \texttt{type},
\texttt{publication} or \texttt{department}. Especially the latter might
be valuable when disambiguating homonymous or polysemous words. For
example, consider the item
\texttt{https://edoc.unibas.ch/id/eprint/76510} which is titled
``Blacking Out.'' Without further context, this title could refer
(amongst others) to a physiological phenomenon, a sudden loss of
electricity, or a measure taken in wartime. Knowing that the item was
published by a researcher employed by the Faculty of Business and
Economics (and not, say, by the Faculty of Medicine) gives us reason to
exclude the first meaning. However, this idea cannot be implemented with
the out of the box instance of Annif employed in this chapter (see
\protect\hyperlink{machine-indexing}{subsection ``Machine indexing''}).

@@

Taking into account the third constraint simply means that we do not
employ any further restrictions. We can hence construct the sample data
set by choosing exactly those items from \texttt{/edoc/raw} which have
non-empty data fields \texttt{title}, \texttt{abstract},
\texttt{id\_number}, and \texttt{keywords}. We do so by calling
\texttt{Data.select\_from\_file} iteratively for all files in
\texttt{/edoc/raw}. The resulting file is saved in
\texttt{/edoc/selected} as \texttt{selected\_master.json}.

@@

Of the 68'345 items in \texttt{/edoc/raw}, all have a title (non-empty
\texttt{title} data field), a little more than half of the items have an
abstract (37'381 items with non-empty \texttt{abstract} data field),
roughly half of the items have an ID (35'355 items with non-empty
\texttt{id\_number} data field),\footnote{Note that when using the facet
  by blank on \texttt{id\_number} in OpenRefine, there are 57'153
  matches; this is due to the fact that many items with an ID such as
  DOI have secondary or tertiary IDs such as ISI or PMID.} and less than
10\% of the items have keywords (6'660 items with non-empty
\texttt{keywords} data field). The sample data set as requires all the
above data fields to be non-empty;
\texttt{/edoc/sample/sample\_master.json} has 4'111 items and hence
constitutes 6\% of the raw data.

@@

\begin{figure}
\centering
\includegraphics{images/chi_square_selection_fields.pdf}
\caption{The sample data set (\(n\) = 4'111) is not representative of
the raw Edoc data per department. Data field \texttt{abstract}:
\(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data field
\texttt{id\_number}: \(\chi^2 (df=9) =\) 4'209.0285, \(p < 0.001\); data
field \texttt{keywords}: \(\chi^2 (df=9) =\) 2'314.533, \(p < 0.001\).
The data foundation is available at
\texttt{/edoc/analysis/chi\_square\_\{data\ field\}} and the
\(\chi^2\)-statistic can be calculated by calling
\texttt{Analysis.print\_chi\_square\_fit} on the data foundation files.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{images/raw_sample_analysis.pdf}
\caption{The sample data set (\(n\) = 4'111) is significantly skewed
towards English (data field \texttt{language}: \(\chi^2 (df=3) =\)
1'441.414, \(p < 0.001\)) journal publications (data field
\texttt{type}: \(\chi^2 (df=10) =\) 52'519.743, \(p < 0.001\)) in the
sciences, medicine and economics (data field \texttt{department}:
\(\chi^2 (df=9) =\) 14'447.276, \(p < 0.001\)) from the 21st century
(data field \texttt{date}: \(\chi^2 (df=7) =\) 35'878.493,
\(p < 0.001\)) as compared to the raw Edoc data. The data foundation is
available at \texttt{/edoc/analysis/chi\_square\_\{data\ field\}} and
the \(\chi^2\)-statistic can be calculated by calling
\texttt{Analysis.print\_chi\_square\_fit} on the data foundation files.}
\end{figure}

@@

\hypertarget{general-overview}{%
\subsection{General overview}\label{general-overview}}

!! Give an overview over machine indexing.

@@

!! Given an intro to Annif. Explain that we are using the out of the box
version

@@

With these improvements in place, each keyword with a suggestion was
assigned a QID via the ``Add cloumns from reconciled values''-function
(and similar for YSO and MeSH identifiers). The data was then exported
and saved as \texttt{/keywords/keywords\_reference.json}. Keywords with
a QID now constitute 69\% of all keywords and 78\% of their total
occurrences in the sample data set, but these numbers are significantly
lower for the MeSH identifier (53.6\% of all keywords with only 28.8\%
of all occurrences) and especially low for the YSO identifier (26.9\% of
all keywords with 11\% of all occurrences). In both cases, the problem
is due to the fact that Wikidata's mapping of MeSH respectively YSO is
only partial. There can be two reasons for this state of affairs for a
given entry: either there is no match between Wikidata and YSO or MeSH
(after all, Wikidata is much larger than MeSH and YSO taken together),
or there is a match but it has not yet been added to the mapping. In the
latter case, at least with respect to YSO, there is a solution: Finto
provides a REST-sytle API to access the YSO vocabulary directly (see
https://api.finto.fi/). For each keyword in the list of reference
keywords that lacks a YSO identifier, the Finto API is queried; if a
term turns up, it is added to the keyword. The effect of this second
reconcilement is detailed in Figure 4. It is achieved by calling
\texttt{Keywords.enrich\_with\_yso} on
\texttt{/keywords/keywords\_reference.json} and saving the output as
\texttt{/keywords/keywords\_reference\_master.json}

@@

Let us now look at the results. First consider the distribution of the
performance scores across departments as shown in Figure 11. We can see
that there are striking differences in variability between departments.
The departments with the most consistent weighted F1-scores are Medicine
and Central Services. However, these two departments have also the
lowest maximum weighted F1-scores. It is noteworthy that all other
departments have maximum weighted F1-scores that are well above the
F1-score of 0.517 of the best performing general Annif configuration.

@@

>>>>

In this section I will\ldots{}

\hypertarget{problem-statement-and-goal}{%
\subsection{Problem statement and
goal}\label{problem-statement-and-goal}}

Edoc is the institutional repository of the University of Basel. It runs
on the EPrints 3 document management system
(https://github.com/eprints/eprints). Edoc was conceived in 2009 as
repository for electronic dissertations and grew in scope when the
University of Basel adapted its first open access policy in 2013. Today
Edoc contains roughly 68'000 items, most of them journal articles
without full text support. Even though descriptive and administrative
metadata are collected for each item, this does not include subject
terms. The lack of subject indexing hampers the repository's usability
and potential with respect to the topic-based monitoring of research
output and, to a lesser extent, information retrieval. The goal of this
project is to remedy this situation with the help of machine indexing.

!! More precisely, this project aims to provide a roadmap for indexing
the elements of Edoc with Annif (Suominen, 2018) -- an open source tool
for automated subject indexing and classification -- and BARTOC FAST
(Hindermann and Ledl, 2020), a federated asynchronous search tool that
covers concepts of thousands of knowledge organization systems like
thesauri, classifications etc.

!! The goal of this thesis is to investigate to what extent machine
indexing can be used to ameliorate institutional repositories.

@@

In this section, I will describe the Edoc data and how it was extracted.

\hypertarget{edoc-data-extraction}{%
\subsection{Edoc data extraction}\label{edoc-data-extraction}}

Even though Edoc is a public server, its database does not have a
web-ready API. In addition, since Edoc is a production server, its
underlying database cannot be used directly on pain of disturbing the
provided services. The data hence needs to be extracted from Edoc in
order to work with it. This could for example be achieved by cloning the
database of the server and running it on a local machine. However, this
route was not available due to the limited resources of the responsible
co-workers. I thus employed a workaround: Edoc has a built-in advanced
search tool where the results can be exported. Even though it is not
possible to extract all database items by default, only one of the many
available search fields has to be filled in. The complete database can
hence be extracted by only filling in the \texttt{date} field and using
a sufficiently permissive time period such as 1940 to 2020 since the
oldest record in the database was published in 1942. On January 21 2021,
this query yielded 68'345 results. These results were then exported as a
326 MB JSON file called \texttt{1942-2020.json}. \texttt{1942-2020.json}
has two drawbacks. First, the maximum file size on GitHub is 100 MB. And
second, \texttt{1942-2020.json} is too big to be handled by standard
editors requiring special editors such as Oxygen. For these reasons
\texttt{1942-2020.json} was split into smaller files that are easier
handled and can be uploaded to GitHub. For this
\texttt{Utility.split\_json} was used yielding 14 files of size 20 MB or
less containing 5000 or fewer entries each. These files are called
\texttt{raw\_master\_\{year\}.json} and saved under \texttt{/files/raw}.

\hypertarget{data-description}{%
\subsection{Data description}\label{data-description}}

Each Edoc item has 43 main data fields. Most of these data fields belong
to the class of descriptive metadata. The data entry for an item's
descriptive metadata is undertaken by the person who uploads the item
which is in most cases one of the item's authors. The Note that an item
is first uploaded to the University of Basel's research database
(https://www.forschdb2.unibas.ch) before being automatically fed into
Edoc. There are explicit rules on how to enter the data as summarized in
the user manual (Universität Basel, n.d.). However, there is no (or at
least no systematic) manual or automatic validation of the entered data.
This means that some data fields are very heterogenous and require
further parsing (see \protect\hyperlink{gold-standard}{section ``Gold
standard''}). The data fields that are of interest to the project at
hand are discussed in more detail in (see
\protect\hyperlink{sample-data-set}{section ``Sample data set''} below).

@@

In this section, I will explain how the sample data set is selected and
constructed. ``Selection'' hereby means the task of specifying a subset
of the Edoc data; by ``construction'' I mean the task of implementing
this selection.

@@

The first constraint is that each item in the sample data set needs to
have a text. Intuitively, this text could consist of a title, an
abstract, or even a full text, or any combination of the above. Similar
to manual indexing, having more information (that is, longer texts)
usually implies a higher indexing quality in machine indexing. However,
this assumption needs to be confirmed empirically for the given machine
indexing framework and data set. If indeed confirmed, it might be
advisable only to index items that have a certain minimal text length.
Therefore, in order to construct the sample data set, we require each
item to have a non-empty value in the data fields \texttt{title},
\texttt{abstract}, and \texttt{id\_number} as proxy to retrieve a full
text remotely. Note that even more context could be provided by taking
into account other data fields such as \texttt{type},
\texttt{publication} or \texttt{department}. Especially the latter might
be valuable when disambiguating homonymous or polysemous words. For
example, consider the item
\texttt{https://edoc.unibas.ch/id/eprint/76510} which is titled
``Blacking Out.'' Without further context, this title could refer
(amongst others) to a physiological phenomenon, a sudden loss of
electricity, or a measure taken in wartime. Knowing that the item was
published by a researcher employed by the Faculty of Business and
Economics (and not, say, by the Faculty of Medicine) gives us reason to
exclude the first meaning. However, this idea cannot be implemented with
the out of the box instance of Annif employed in this chapter (see
\protect\hyperlink{machine-indexing}{section ``Machine indexing''}).

@@

Taking into account the third constraint simply means that we do not
employ any further restrictions. We can hence construct the sample data
set by choosing exactly those items from \texttt{/files/raw} which have
non-empty data fields \texttt{title}, \texttt{abstract},
\texttt{id\_number}, and \texttt{keywords}. We do so by calling
\texttt{Data.select\_from\_file} iteratively for all files in
\texttt{/files/raw}. The resulting file is saved in
\texttt{/files/selected} as \texttt{selected\_master.json}.

@@

\begin{figure}
\centering
\includegraphics{images/chi_square_selection_fields.pdf}
\caption{The sample data set (\(n\) = 4'111) is not representative of
the raw Edoc data per department. Data field \texttt{abstract}:
\(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data field
\texttt{id\_number}: \(\chi^2 (df=9) =\) 4'209.0285, \(p < 0.001\); data
field \texttt{keywords}: \(\chi^2 (df=9) =\) 2'314.533, \(p < 0.001\).
The data foundation is available at
\texttt{/files/analysis/chi\_square\_\{data\ field\}} and the
\(\chi^2\)-statistic can be calculated by calling
\texttt{Analysis.print\_chi\_square\_fit} on the data foundation files.}
\end{figure}

Of the 68'345 items in \texttt{/files/raw}, all have a title (non-empty
\texttt{title} data field), a little more than half of the items have an
abstract (37'381 items with non-empty \texttt{abstract} data field),
roughly half of the items have an ID (35'355 items with non-empty
\texttt{id\_number} data field),\footnote{Note that when using the facet
  by blank on \texttt{id\_number} in OpenRefine, there are 57'153
  matches; this is due to the fact that many items with an ID such as
  DOI have secondary or tertiary IDs such as ISI or PMID.} and less than
10\% of the items have keywords (6'660 items with non-empty
\texttt{keywords} data field). The sample data set as requires all the
above data fields to be non-empty;
\texttt{/files/sample/sample\_master.json} has 4'111 items and hence
constitutes 6\% of the raw data.

@@

@@

\begin{figure}
\centering
\includegraphics{images/raw_sample_analysis.pdf}
\caption{The sample data set (\(n\) = 4'111) is significantly skewed
towards English (data field \texttt{language}: \(\chi^2 (df=3) =\)
1'441.414, \(p < 0.001\)) journal publications (data field
\texttt{type}: \(\chi^2 (df=10) =\) 52'519.743, \(p < 0.001\)) in the
sciences, medicine and economics (data field \texttt{department}:
\(\chi^2 (df=9) =\) 14'447.276, \(p < 0.001\)) from the 21st century
(data field \texttt{date}: \(\chi^2 (df=7) =\) 35'878.493,
\(p < 0.001\)) as compared to the raw Edoc data. The data foundation is
available at \texttt{/files/analysis/chi\_square\_\{data\ field\}} and
the \(\chi^2\)-statistic can be calculated by calling
\texttt{Analysis.print\_chi\_square\_fit} on the data foundation files.}
\end{figure}

@@

In this section, I will briefly introduce Annif and how indexing with
Annif was implemented. For a general overview concerning machine
indexing, see Golub (2019).

@@

Annif (Suominen et al. 2021) is an open source multi-algorithm automated
indexing tool developed at the Finnish National Library (see Suominen
2019 for an overview). Training a local Annif instance for machine
indexing is currently evaluated at different libraries, for example at
the German National Library (Nagelschmidt 12.11.2020). As stated in
section \protect\hyperlink{introduction}{section ``Introduction''}, in
this project I am interested in using Annif out of the box. This means
that instead of training a local Annif instance, I will be relying on
the Annif REST-style API (see https://api.annif.org/).\footnote{This API
  is specifically intended for testing. For integration into a
  production system, the Finto AI API is available (see
  https://ai.finto.fi/v1/ui/).} The advantage of this approach is that
it is quick and relatively easy to implement. The disadvantage is that
no custom algorithms or vocabularies can be used. The task of
constructing a gold standard (see
\protect\hyperlink{gold-standard}{section ``Gold standard''}) remains
the same.

@@

With these improvements in place, each keyword with a suggestion was
assigned a QID via the ``Add cloumns from reconciled values''-function
(and similar for YSO and MeSH identifiers). The data was then exported
and saved as \texttt{/keywords/keywords\_reference.json}. Keywords with
a QID now constitute 69\% of all keywords and 78\% of their total
occurrences in the sample data set, but these numbers are significantly
lower for the MeSH identifier (53.6\% of all keywords with only 28.8\%
of all occurrences) and especially low for the YSO identifier (26.9\% of
all keywords with 11\% of all occurrences). In both cases, the problem
is due to the fact that Wikidata's mapping of MeSH respectively YSO is
only partial. There can be two reasons for this state of affairs for a
given entry: either there is no match between Wikidata and YSO or MeSH
(after all, Wikidata is much larger than MeSH and YSO taken together),
or there is a match but it has not yet been added to the mapping. In the
latter case, at least with respect to YSO, there is a solution: Finto
provides a REST-style API to access the YSO vocabulary directly (see
https://api.finto.fi/). For each keyword in the list of reference
keywords that lacks a YSO identifier, the Finto API is queried; if a
term turns up, it is added to the keyword. The effect of this second
reconcilement is detailed in Figure 4. It is achieved by calling
\texttt{Keywords.enrich\_with\_yso} on
\texttt{/keywords/keywords\_reference.json} and saving the output as
\texttt{/keywords/keywords\_reference\_master.json}

@@

Let us now look at the results. First consider the distribution of the
performance scores across departments as shown in Figure 11. We can see
that there are striking differences in variability between departments.
The departments with the most consistent weighted F1-scores are Medicine
and Central Services. However, these two departments have also the
lowest maximum weighted F1-scores. It is noteworthy that all other
departments have maximum weighted F1-scores that are well above the
weighted F1-score of 0.517 of the best performing general Annif
configuration.

@@

Codebase available at: \url{https://github.com/MHindermann/mas}

\hypertarget{class-files.utility}{%
\subsection{class files.Utility()}\label{class-files.utility}}

A collection of utility functions.

\hypertarget{classmethod-load_jsonfile_path}{%
\subsubsection{classmethod
load\_json(file\_path)}\label{classmethod-load_jsonfile_path}}

Load a JSON object from file.

\begin{itemize}
\item
  \textbf{Parameters}

  \textbf{file\_path} (\texttt{str}) -- complete path to file including
  filename and extension
\item
  \textbf{Return type}

  \texttt{list}
\end{itemize}

\hypertarget{classmethod-save_jsondata-file_path}{%
\subsubsection{classmethod save\_json(data,
file\_path)}\label{classmethod-save_jsondata-file_path}}

Save data as JSON file.

\begin{itemize}
\item
  \textbf{Parameters}

  \begin{itemize}
  \item
    \textbf{data} (\texttt{Union}{[}\texttt{List}, \texttt{Dict}{]}) --
    the data to be saved
  \item
    \textbf{file\_path} (\texttt{str}) -- complete path to file
    including filename and extension
  \end{itemize}
\item
  \textbf{Return type}

  \texttt{None}
\end{itemize}

\hypertarget{classmethod-split_jsonfile_path-save_path}{%
\subsubsection{classmethod split\_json(file\_path,
save\_path)}\label{classmethod-split_jsonfile_path-save_path}}

Split a JSON file into files not larger than 100MB.

\begin{itemize}
\item
  \textbf{Parameters}

  \begin{itemize}
  \item
    \textbf{file\_path} (\texttt{str}) -- complete path to file
    including filename and extension
  \item
    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
    including filename without extension
  \end{itemize}
\item
  \textbf{Return type}

  \texttt{None}
\end{itemize}

\hypertarget{class-files.data}{%
\subsection{class files.Data()}\label{class-files.data}}

A collection of Edoc data functions.

\hypertarget{classmethod-enrich_author_keywordsfile_path-save_path}{%
\subsubsection{classmethod enrich\_author\_keywords(file\_path,
save\_path)}\label{classmethod-enrich_author_keywordsfile_path-save_path}}

Enrich author keywords.

For each Edoc item: the string of author keywords is cut into single
keywords and each keyword is cleaned. Each keyword is then enriched with
Qid, MeSH and YSO ID if available.

\begin{itemize}
\item
  \textbf{Parameters}

  \begin{itemize}
  \item
    \textbf{file\_path} (\texttt{str}) -- complete path to file
    including filename and extension
  \item
    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
    including filename without extension
  \end{itemize}
\item
  \textbf{Return type}

  \texttt{None}
\end{itemize}

\hypertarget{classmethod-enrich_with_anniffile_path-save_path-project_ids-abstractfalse-fulltextfalse-limitnone-thresholdnone}{%
\subsubsection{classmethod enrich\_with\_annif(file\_path, save\_path,
project\_ids, abstract=False, fulltext=False, limit=None,
threshold=None)}\label{classmethod-enrich_with_anniffile_path-save_path-project_ids-abstractfalse-fulltextfalse-limitnone-thresholdnone}}

Enrich items from file with automatic keywords using Annif-client.

Available Annif-client project IDs are yso-en, yso-maui-en,
yso-bonsai-en, yso-fasttext-en, wikidata-en.

\begin{itemize}
\item
  \textbf{Parameters}

  \begin{itemize}
  \item
    \textbf{file\_path} (\texttt{str}) -- complete path to file
    including filename and extension
  \item
    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
    including filename without extension
  \item
    \textbf{project\_ids} (\texttt{List}{[}\texttt{str}{]}) --
    Annif-client project IDs to be used
  \item
    \textbf{abstract} (\texttt{bool}) -- toggle use abstract for
    indexing, defaults to False
  \item
    \textbf{fulltext} (\texttt{bool}) -- toggle use fulltext for
    indexing, defaults to False
  \item
    \textbf{limit} (\texttt{Optional}{[}\texttt{int}{]}) -- Annif-client
    limit, defaults to None
  \item
    \textbf{threshold} (\texttt{Optional}{[}\texttt{int}{]}) --
    Annif-client threshold, defaults to None
  \end{itemize}
\item
  \textbf{Return type}

  \texttt{None}
\end{itemize}

\hypertarget{classmethod-enrich_with_meshfile_path-save_path}{%
\subsubsection{classmethod enrich\_with\_mesh(file\_path,
save\_path)}\label{classmethod-enrich_with_meshfile_path-save_path}}

Enrich Edoc data per item with MeSH keywords from PubMed if available.

\begin{itemize}
\item
  \textbf{Parameters}

  \begin{itemize}
  \item
    \textbf{file\_path} (\texttt{str}) -- complete path to file
    including filename and extension
  \item
    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
    including filename without extension
  \end{itemize}
\item
  \textbf{Return type}

  \texttt{None}
\end{itemize}

\hypertarget{classmethod-fetch_meshpubmed_id}{%
\subsubsection{classmethod
fetch\_mesh(pubmed\_id)}\label{classmethod-fetch_meshpubmed_id}}

Fetch MeSH keywords for article based on PubMed ID.

\begin{itemize}
\item
  \textbf{Parameters}

  \textbf{pubmed\_id} (\texttt{str}) -- article PubMed ID
\item
  \textbf{Return type}

  \texttt{List}{[}\texttt{Dict}{]}
\end{itemize}

\hypertarget{classmethod-get_departments}{%
\subsubsection{classmethod
get\_departments()}\label{classmethod-get_departments}}

Get all Edoc departments.

\begin{itemize}
\item
  \textbf{Return type}

  \texttt{List}{[}\texttt{str}{]}
\end{itemize}

\hypertarget{classmethod-inspectdata-fields}{%
\subsubsection{classmethod inspect(data,
*fields)}\label{classmethod-inspectdata-fields}}

Print fields of items in data.

\begin{itemize}
\item
  \textbf{Parameters}

  \begin{itemize}
  \item
    \textbf{data} (\texttt{List}{[}\texttt{Dict}{]}) -- data to be
    inspected
  \item
    \textbf{fields} (\texttt{str}) -- fields to focus on
  \end{itemize}
\item
  \textbf{Return type}

  \texttt{None}
\end{itemize}

\hypertarget{classmethod-map2referencekeyword}{%
\subsubsection{classmethod
map2reference(keyword)}\label{classmethod-map2referencekeyword}}

Map a keyword to its reference keyword.

Keyword must first be cleaned by corresponding \_Keyword method.

\begin{itemize}
\item
  \textbf{Parameters}

  \textbf{keyword} (\texttt{str}) -- the keyword
\item
  \textbf{Return type}

  \texttt{Dict}
\end{itemize}

\hypertarget{classmethod-select_from_datadata-fields}{%
\subsubsection{classmethod select\_from\_data(data,
*fields)}\label{classmethod-select_from_datadata-fields}}

Select items from data based on non-empty fields.

Only items where all required fields are non-empty are sample.

\begin{itemize}
\item
  \textbf{Parameters}

  \begin{itemize}
  \item
    \textbf{data} (\texttt{List}{[}\texttt{Dict}{]}) -- the input data
  \item
    \textbf{fields} (\texttt{str}) -- the required fields for an item to
    be sample
  \end{itemize}
\item
  \textbf{Return type}

  \texttt{List}{[}\texttt{Dict}{]}
\end{itemize}

\hypertarget{classmethod-select_from_filefile_path-fields}{%
\subsubsection{classmethod select\_from\_file(file\_path,
*fields)}\label{classmethod-select_from_filefile_path-fields}}

Select items from file according to fields.

For example: select\_from\_file(DIR + ``/raw/2019.json,'' ``title,''
``abstract,'' ``keywords,'' ``id\_number'')

\begin{itemize}
\item
  \textbf{Parameters}

  \begin{itemize}
  \item
    \textbf{file\_path} (\texttt{str}) -- complete path to file
    including filename and extension
  \item
    \textbf{fields} (\texttt{str}) -- the required fields for an item to
    be sample
  \end{itemize}
\item
  \textbf{Return type}

  \texttt{None}
\end{itemize}

\hypertarget{classmethod-super_enrich_with_annifabstract}{%
\subsubsection{classmethod
super\_enrich\_with\_annif(abstract)}\label{classmethod-super_enrich_with_annifabstract}}

Enrich items with automatic keywords using all Annif-client projects.

\begin{itemize}
\item
  \textbf{Parameters}

  \textbf{abstract} (\texttt{bool}) -- toggle use abstract for indexing
\item
  \textbf{Return type}

  \texttt{None}
\end{itemize}

\hypertarget{class-files.keywords}{%
\subsection{class files.Keywords()}\label{class-files.keywords}}

A collection of functions for manipulating Edoc author keywords.

\hypertarget{classmethod-clean_keywordkeyword}{%
\subsubsection{classmethod
clean\_keyword(keyword)}\label{classmethod-clean_keywordkeyword}}

Clean a keyword.

\begin{itemize}
\item
  \textbf{Parameters}

  \textbf{keyword} (\texttt{str}) -- the keyword
\item
  \textbf{Return type}

  \texttt{List}{[}\texttt{str}{]}
\end{itemize}

\hypertarget{classmethod-clean_keywordskeywords_per_item}{%
\subsubsection{classmethod
clean\_keywords(keywords\_per\_item)}\label{classmethod-clean_keywordskeywords_per_item}}

Turn a string of keywords per item into a list of cleaned (=normalized)
keywords.

\begin{itemize}
\item
  \textbf{Parameters}

  \textbf{keywords\_per\_item} (\texttt{List}{[}\texttt{str}{]}) -- the
  keywords
\item
  \textbf{Return type}

  \texttt{List}{[}\texttt{str}{]}
\end{itemize}

\hypertarget{classmethod-enrich_with_ysofile_path-save_path}{%
\subsubsection{classmethod enrich\_with\_yso(file\_path,
save\_path)}\label{classmethod-enrich_with_ysofile_path-save_path}}

Blah.

\begin{itemize}
\item
  \textbf{Parameters}

  \begin{itemize}
  \item
    \textbf{file\_path} (\texttt{str}) -- complete path to file
    including filename and extension
  \item
    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
    including filename without extension
  \end{itemize}
\end{itemize}

\hypertarget{classmethod-extract_keywordsfile_path}{%
\subsubsection{classmethod
extract\_keywords(file\_path)}\label{classmethod-extract_keywordsfile_path}}

Extract keywords per item from file.

\begin{itemize}
\item
  \textbf{Parameters}

  \textbf{file\_path} (\texttt{str}) -- complete path to file including
  filename and extension
\item
  \textbf{Return type}

  \texttt{List}{[}\texttt{str}{]}
\end{itemize}

\hypertarget{classmethod-fetch_ysokeyword}{%
\subsection{classmethod
fetch\_yso(keyword)}\label{classmethod-fetch_ysokeyword}}

Fetch the YSO ID for a keyword if any.

\begin{itemize}
\item
  \textbf{Parameters}

  \textbf{keyword} (\texttt{str}) -- the keyword
\item
  \textbf{Return type}

  \texttt{Optional}{[}\texttt{str}{]}
\end{itemize}

\hypertarget{classmethod-make_countfile_path-save_path}{%
\subsubsection{classmethod make\_count(file\_path,
save\_path)}\label{classmethod-make_countfile_path-save_path}}

Count all keywords and their respective IDs per item in file.

\begin{itemize}
\item
  \textbf{Parameters}

  \begin{itemize}
  \item
    \textbf{file\_path} (\texttt{str}) -- complete path to file
    including filename and extension
  \item
    \textbf{save\_path} (\texttt{str}) -- complete path to save folder
    including filename and extension
  \end{itemize}
\item
  \textbf{Return type}

  \texttt{None}
\end{itemize}

\hypertarget{classmethod-make_histogramkeywords}{%
\subsubsection{classmethod
make\_histogram(keywords)}\label{classmethod-make_histogramkeywords}}

Make a histogram for keywords.

\begin{itemize}
\item
  \textbf{Parameters}

  \textbf{keywords} (\texttt{List}{[}\texttt{str}{]}) -- the keywords
\item
  \textbf{Return type}

  \texttt{List}{[}\texttt{Dict}{]}
\end{itemize}

\hypertarget{class-files.analysis}{%
\subsection{class files.Analysis()}\label{class-files.analysis}}

A collection of data analysis functions.

\hypertarget{classmethod-count_confusionstandard-suggestions}{%
\subsubsection{classmethod count\_confusion(standard,
suggestions)}\label{classmethod-count_confusionstandard-suggestions}}

Count the values in the confusion matrix for standard and suggestions.

\begin{itemize}
\item
  \textbf{Parameters}

  \begin{itemize}
  \item
    \textbf{standard} (\texttt{list}) -- the standard
  \item
    \textbf{suggestions} (\texttt{list}) -- the suggestions
  \end{itemize}
\end{itemize}

\hypertarget{classmethod-extract_standarditem-marker}{%
\subsubsection{classmethod extract\_standard(item,
marker)}\label{classmethod-extract_standarditem-marker}}

Extract gold standard IDs from item.

\begin{itemize}
\item
  \textbf{Parameters}

  \begin{itemize}
  \item
    \textbf{item} (\texttt{dict}) -- the Edoc item
  \item
    \textbf{marker} (\texttt{str}) -- the type of ID
  \end{itemize}
\item
  \textbf{Return type}

  \texttt{Optional}{[}\texttt{list}{]}
\end{itemize}

\hypertarget{classmethod-extract_suggestionsitem-marker-n10}{%
\subsubsection{classmethod extract\_suggestions(item, marker,
n=10)}\label{classmethod-extract_suggestionsitem-marker-n10}}

Extract top n Annif suggestion IDs from item.

\begin{itemize}
\item
  \textbf{Parameters}

  \begin{itemize}
  \item
    \textbf{item} (\texttt{dict}) -- the Edoc item
  \item
    \textbf{marker} (\texttt{str}) --
    project\_id-abstract-fulltext-limit-threshold
  \item
    \textbf{n} (\texttt{int}) -- number of top IDs (by score) to be
    extracted, defaults to 10
  \end{itemize}
\end{itemize}

\hypertarget{classmethod-get_id_typemarker}{%
\subsubsection{classmethod
get\_id\_type(marker)}\label{classmethod-get_id_typemarker}}

Get the ID type from the project ID.

\begin{itemize}
\item
  \textbf{Parameters}

  \textbf{marker} (\texttt{str}) --
  project\_id-abstract-fulltext-limit-threshold
\item
  \textbf{Return type}

  \texttt{str}
\end{itemize}

\hypertarget{classmethod-get_sklearn_arrayitem-project_id-abstractfalse-fulltextfalse-limitnone-thresholdnone-n10}{%
\subsubsection{classmethod get\_sklearn\_array(item, project\_id,
abstract=False, fulltext=False, limit=None, threshold=None,
n=10)}\label{classmethod-get_sklearn_arrayitem-project_id-abstractfalse-fulltextfalse-limitnone-thresholdnone-n10}}

Get Sklearn y\_true and y\_pred for an item.

Available Annif-client project IDs are yso-en, yso-maui-en,
yso-bonsai-en, yso-fasttext-en, wikidata-en.

\begin{itemize}
\item
  \textbf{Parameters}

  \begin{itemize}
  \item
    \textbf{item} (\texttt{dict}) -- sample data set item
  \item
    \textbf{project\_id} (\texttt{str}) -- Annif-client project ID
  \item
    \textbf{abstract} (\texttt{bool}) -- toggle use abstract for
    indexing, defaults to False
  \item
    \textbf{fulltext} (\texttt{bool}) -- toggle use fulltext for
    indexing, defaults to False
  \item
    \textbf{limit} (\texttt{Optional}{[}\texttt{int}{]}) -- Annif-client
    limit, defaults to None
  \item
    \textbf{threshold} (\texttt{Optional}{[}\texttt{int}{]}) --
    Annif-client threshold, defaults to None
  \item
    \textbf{n} (\texttt{int}) -- number of top IDs (by score) to be
    extracted, defaults to 10
  \end{itemize}
\item
  \textbf{Return type}

  \texttt{Optional}{[}\texttt{dict}{]}
\end{itemize}

\hypertarget{classmethod-make_metricsfile_path-project_id-abstractfalse-fulltextfalse-limitnone-thresholdnone-n10-departmentnone}{%
\subsubsection{classmethod make\_metrics(file\_path, project\_id,
abstract=False, fulltext=False, limit=None, threshold=None, n=10,
department=None)}\label{classmethod-make_metricsfile_path-project_id-abstractfalse-fulltextfalse-limitnone-thresholdnone-n10-departmentnone}}

Make Sklearn metrics F1, recall, precision for file.
